Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
red marks

\section{The Problem and Baseline approach}
We are interested in designing a mechanism for privately releasing
\emph{fully} the posterior distributions derived in section \ref{sec_background},
and not a sample from them.  It's worth noticing that the posterior
distributions are fully characterized by their parameters, and the
family (beta, Dirichlet) they belong to.  Hence, in case of the
Beta-Binomial model we are interested in releasing a private version
of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a
private version of $\valpha'=(\valpha + \Delta \valpha)$.  \cite{} and \cite{} have
already attacked this problem and their solution consisted in adding
independent Laplacian noise to the parameters of the posteriors. That
is, in the case of the Beta-Binomial system the value released would
be: $(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
%with truncating method come from algorithm designed by \citet{zhang2016differential}
Where $Lap(\mu,\nu)$
denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^{n}$ we say that $\dataobs$ and $\dataobs'$ are adjacent iff
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$.} data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

\noindent Also, in previous works, the accuracy has been measured again with respect to
$\ell_1$ norm. That is, a lower bound has been given to
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance, which for two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1), \boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is defined as
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)\equiv
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
\section{Technical Problem Statement}
\label{sec_bayesInfer}
The posterior belief about parameters $\xis$ is inferred from the
group of sensitive data. Because it is usually published in form of a
distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
can relieve a lot of information about sensitive data. So, the
sensitive information we want to protect here is the posterior belief,
i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
it\cite{foulds2016theory}. Then it will be better if we can use a
distance over two distributions to measure the accuracy than a
distance over just parameters or values when we are protecting a
distribution, for instance, Hellinger distance in our paper. When we
measure the accuracy between true posterior and protected posterior
using Hellinger distance, it would be better we can have a protection
mechanism based on Hellinger distance. However, current mechanisms are
mainly based on $l_1$ norm by Laplace mechanism
\cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
design our exponential mechanism over Hellinger distance to protect
the whole posterior distribution.

>>>>

\section{The Problem and Baseline approach}
We are interested in designing a mechanism for privately releasing
\emph{fully} the posterior distributions derived in section \ref{sec_background},
and not a sample from them.  It's worth noticing that the posterior
distributions are fully characterized by their parameters, and the
family (beta, Dirichlet) they belong to.  Hence, in case of the
Beta-Binomial model we are interested in releasing a private version
of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a
private version of $\valpha'=(\valpha + \Delta \valpha)$. \todo{ \cite{?} and \cite{?}} have
already attacked this problem and their solution consisted in adding
independent Laplacian noise to the parameters of the posteriors. That
is, in the case of the Beta-Binomial system the value released would
be: $(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
%with truncating method come from algorithm designed by \citet{zhang2016differential}
Where $Lap(\mu,\nu)$
denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^{n}$ we say that $\dataobs$ and $\dataobs'$ are adjacent iff
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$.} data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

\noindent Also, in previous works, the accuracy has been measured again with respect to
$\ell_1$ norm. That is, a lower bound has been given to
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance, which for two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1), \boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is defined as
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)\equiv
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
% \section{Technical Problem Statement}
% \label{sec_bayesInfer}
% The posterior belief about parameters $\xis$ is inferred from the
% group of sensitive data. Because it is usually published in form of a
% distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
% can relieve a lot of information about sensitive data. So, the
% sensitive information we want to protect here is the posterior belief,
% i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
% it\cite{foulds2016theory}. Then it will be better if we can use a
% distance over two distributions to measure the accuracy than a
% distance over just parameters or values when we are protecting a
% distribution, for instance, Hellinger distance in our paper. When we
% measure the accuracy between true posterior and protected posterior
% using Hellinger distance, it would be better we can have a protection
% mechanism based on Hellinger distance. However, current mechanisms are
% mainly based on $l_1$ norm by Laplace mechanism
% \cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
% design our exponential mechanism over Hellinger distance to protect
% the whole posterior distribution.
